Optimization of wide-band quasi-omnidirectional 1-D photonic structures

### 2021-05-01 PaperVictor.tex
Corrections of David

% !TeX spellcheck = en_US
\documentclass[a4paper,fleqn]{cas-sc}
\usepackage[numbers]{natbib}
%%%Author macros
\def\tsc#1{\csdef{#1}{\textsc{\lowercase{#1}}\xspace}}
\tsc{WGM}
\tsc{QE}
\tsc{EP}
\tsc{PMS}
\tsc{BEC}
\tsc{DE}
%%%
\usepackage{braket}
\usepackage{bm}
\usepackage{xcolor}
\newcommand{\hl}[1]{{\color{blue}#1}}
\begin{document}
\let\WriteBookmarks\relax
\def\floatpagepagefraction{1}
\def\textpagefraction{.001}
\shorttitle{Optimization of wide-band quasi-omnidirectional 1-D photonic structures}
\shortauthors{V. Castillo-Gallardo et~al.}

@@

\begin{abstract}
We have designed, optimized, fabricated and characterized highly
reflective quasi-omnidirectional (angular range of $0-60^\circ$)
multilayered structures with a wide spectral range. Two techniques,
chirping (a continuous change in thicknesses) and stacking of
Bragg-type sub-structures, have been used to enhance the
reflectance with minimum thickness for a given pair of refractive
indices. Numerical calculations were carried out employing the
transfer matrix method and we optimized the design parameters to
obtain maximal reflectance averaged over different spectral ranges
for all angles. We fabricated some of the optimized structures with
porous silicon dielectric multilayers with low refractive contrast
and compared their measured  optical properties with the
calculations. Two chirped structures with thicknesses 21.6 $\mu$m
and 60.4 $\mu$m, resulting in quasi-omnidirectional mirrors with
bandwidths of 360 nm and 1800 nm, centered at 1160 nm and 1925 nm
respectively have been shown. In addition, we fabricated a stacked
sub-Bragg mirror structure  with a quasi-omnidirectional bandwidth
of 1800 nm centered at 1850 nm and a thickness of 41.5 $\mu$m,
which is almost two third (in thickness) of the chirped structure.
Thus, our techniques allowed us to obtain relatively thin
quasi-omnidirectional mirrors with wide bands over different
wavelength ranges. Our analysis techniques can be used for the
optimization of the reflectance not only in multilayered PS
systems  with different refractive index contrasts but also for
systems with other types of materials with low refractive index
contrast. The present study could also be useful for obtaining
omnidirectional dielectric mirrors in large spectral regions using
different materials,  flat focusing reflectors, thermal regulators,
or, if defects are included, as filters or remote
chemical/biosensors with a wide angular independent response.
\end{abstract}

@@

Photonic crystal (PC)-based structures have been extensively investigated due
to their light controlling properties \cite{Joannopoulos2008,Goyal2018}.
Photons entering a PC interact with its periodically varying dielectric constant and
their energies are consequently organized into photonic bands. In
analogy to electronic bands within a
crystal, propagation is forbidden if the energy lies
within certain regions known as photonic band gaps (PBG's). Thus, the
PC behaves as a mirror if illuminated by light with frequencies
within in a PBG. For several applications it is useful to fabricate
{\em ommnidirectional} mirrors with an absolute band gap for all angles of incidence.
The use of metallic
mirrors is limited due to their relatively large absorption at the
visible (Vis) and near infrared (NIR) frequencies.  An attractive alternative
consists of low-absorption dielectric
structures,  which may be designed for specific frequency
ranges. One-dimensional (1D) and two-dimensional (2D) PCs have
applications in optoelectronics, optical telecommunications and computing,
laser technology \cite{Lopez2003,Masaya2010}, and radiative cooling applications
\cite{Kumar2020}. The simplest 1D-PC is composed of a finite number
of periodically alternating
layers of high $n_{H}$ and low $n_{L}$ refractive indices, with
corresponding thicknesses $d_H$ and $d_L$ chosen so that their optical
thicknesses corresponds to a quarter of a wavelength
$n_{H}d_{H}=n_{L}d_{L}=\lambda_{0}/4$ at a nominal
wavelength $\lambda_{0}$. This yields a {\em Bragg mirror} (BM)
which might have a large PBG including an omnidirectional gap if the contrast $n_H/n_L$
and the number of periods are large enough. Mirrors with high
reflectance within a wider frequency range may be engineered by
using different nominal wavelengths for different layers.
One way to obtain such structures is to gradually change the width of
the layers as a function of their depth, producing
\textit{chirped}-type structures \cite{Zipock1997}.
Another alternative is to stack BMs, in such a way that their reflection bands partially
overlap each other at their edges, resulting in a wider high-reflection band \cite{Xifre2009}.

@@

In Fig. \ref{Fig2}(a) we present the calculated and measured
reflectance for non-polarized light corresponding to sample $S_1$ in the spectral range from 350 to 1400
nm for different angles of
incidence $\theta=10^\circ$, $20^\circ$, $30^\circ$, $40^\circ$,
$50^\circ$, and $60^\circ$. The spectra are qualitatively
similar, and for $\lambda>700$ nm and $10^\circ < \theta <
40^\circ$, they agree quantitatively, with a difference smaller
than $5\%$.
The
measured reflectance is lower than the calculated one, more so at
small wavelengths and large angles. This difference
may be partially attributed to the scattering of light due to the
roughness present at the sample
\cite{Theiss1994,Chavez2020,Ortiz2020} that we have not taken into
account in our theory. Due to the limitations of our
spectrophotometer, we couldn't perform measurements for $\theta>60^\circ$ and thus
check the ODB. Nevertheless, our results allow us to conclude that
the structure has a quasi-ODB from 980 and
1340 nm.
\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{F2Alternativa.pdf}
  \end{center}
  \caption{Reflectance spectra for non-polarized light calculated and measured at different
    angles of incidence $\theta=10^\circ$, $20^\circ$, $30^\circ$,
    $40^\circ$, $50^\circ$, and $60^\circ$ for structure $S_1$
    (panel a)  and $S_2$ (panel b). The gray band indicates the
    region where the reflectance is greater than  $0.90$,
    corresponding to the quasi-ODB of the
    structure. Inset: photograph of the synthesized structure.}
  \label{Fig2}
\end{figure}
In Fig. \ref{Fig2}(b) we compare the
calculated and measured spectra of sample $S_2$ in the range
from 400 to 3000 nm.
Both spectra are very similar, with some differences at long
wavelengths which can be
attributed to an increase of imperfections such as wavy layers and
more roughness for deeper layers, due to a more restricted diffusivity
of the electrolyte as the thickness of the structure is increased
\cite{Negro2003,Vincent1993}. According to our results, this
structure has a wide quasi-ODW of 1800 nm
centered at 1880 nm.

@@

According to Table \ref{tab:table2}, the structure that has the highest
reflectance is in the second block, with an optimal overlap between
consecutive PBGs of $78\%$, a thickness of
41.5 $\mu$m, and an average reflectance $\braket{0.954}$. It is made up
of 18 sub-mirrors tuned to the wavelengths
400, 460, 510, 570, 640, 720, 810, 910, 1020, 1150, 1290, 1450,
1630, 1830, 2060, 2320, 2610, and 2860 nm.
We synthesized this structure and designated it {\em sample $S_3$}.
Its calculated and measured
reflectance spectra are shown in Fig. \ref{Fig3}.
\begin{figure}
        \begin{center}
                \includegraphics[width=\textwidth]
                {F3Alternativa.pdf}
        \end{center}
        \caption{ (a) Calculated reflectance $R(\lambda,\theta)$ for non-polarized light of the optimized structure $S_3$
                as a function of wavelength $\lambda$ and incidence angle
                $\theta$. (b) Measured and calculated reflectance spectra at several
                angles of incidence $\theta=10^\circ$, $20^\circ$,
                $30^\circ$, $40^\circ$, $50^\circ$, $60^\circ$. The gray band indicates
                the region in which the reflectance is greater than $R>0.90$.  Inset shows a
                photograph with a top view of the synthesized structure.}
        \label{Fig3}
\end{figure}

@@

We have designed, optimized, fabricated and characterized highly
reflective quasi-omnidirectional (angular range of $0-60^\circ$)
multilayered structures with a wide
spectral range. Two techniques, chirping (a continuous change in thicknesses) and
stacking of Bragg-type sub-structures, have been used to enhance the
reflectance with minimum thickness for a given pair of refractive
indices. Numerical calculations were
carried out employing a stabilized transfer matrix method and we optimized the
design parameters to obtain maximal reflectance averaged over different spectral ranges for
all angles.
We fabricated some of the optimized structures with
porous silicon
dielectric multilayers with low refractive contrast and compared their measured  optical properties
with the calculations. Two chirped structures
with thicknesses 21.6 $\mu$m and 60.4 $\mu$m,
resulting in quasi-omnidirectional mirrors with bandwidths of 360 nm and 1800 nm, centered
at 1160 nm and 1925 nm respectively have been shown. In addition,
we fabricated a stacked sub-Bragg mirror structure  with a
quasi-omnidirectional bandwidth of 1800 nm centered at 1850 nm and a
thickness of 41.5 $\mu$m, which is almost two thirds as thick as the chirped structure.
Thus, our techniques allowed us to obtain relatively thin
quasi-omnidirectional mirrors with wide bands
over different wavelength ranges.
Our analysis techniques can
be used for the optimization of the reflectance not only in multilayered PS systems with
different refractive index contrasts but also for systems with other types of
materials with low refractive index contrast. The present study could
also be useful for obtaining omnidirectional dielectric mirrors in
large spectral regions using different materials,  flat focusing
reflectors, thermal regulators, or, if
defects are included, as filters or remote chemical/biosensors with
a wide angular independent response.

@@

\bibliographystyle{unsrt}
\bibliography{Bibliografia}

>>>>

% !TeX spellcheck = en_US
\documentclass[a4paper,fleqn]{cas-sc}
\usepackage[numbers,sort&compress]{natbib}
%%%Author macros
\def\tsc#1{\csdef{#1}{\textsc{\lowercase{#1}}\xspace}}
\tsc{WGM}
\tsc{QE}
\tsc{EP}
\tsc{PMS}
\tsc{BEC}
\tsc{DE}
%%%
%\usepackage{cite}
\usepackage{braket}
\usepackage{bm}
\usepackage{xcolor}
\newcommand{\hl}[1]{{\color{blue}#1}}
\begin{document}
\bibliographystyle{unsrt}
\let\WriteBookmarks\relax
\def\floatpagepagefraction{1}
\def\textpagefraction{.001}
\shorttitle{Optimization of wide-band quasi-omnidirectional 1-D photonic structures}
\shortauthors{V. Castillo-Gallardo et~al.}

@@

\begin{abstract}
We design, optimize, fabricate, and characterize highly
reflective quasi-omnidirectional multilayered structures with a wide
angular and spectral range. We consider chirped structures with layers
of gradually varying thicknesses and structures made by stacking
Bragg-type sub-structures, and we maximized their numerically calculated
reflectance averaged over different spectral ranges keeping a minimum
thickness for given pairs of refractive indices. We fabricated some of
these structures with porous silicon with a low refractive contrast
between adjacent layers,
and compared their measured  optical properties to the theoretical
results and to previous works. We obtained relatively thin
quasi-omnidirectional mirrors with wide bands over different
wavelength ranges that compare favorably to others reported in the
literature.

\end{abstract}

@@

Photonic crystal (PC)-based structures have been extensively investigated due
to their light controlling properties \cite{Joannopoulos2008,Goyal2018}.
Photons entering a PC interact with its periodically varying dielectric constant and
their energies are consequently organized into photonic bands. In
analogy to electronic bands within a
crystal, propagation is forbidden if the energy lies
within certain regions known as photonic band gaps (PBG's). Thus, the
PC behaves as a mirror if illuminated by light with frequencies
within in a PBG. For several applications it is useful to fabricate
{\em ommnidirectional} mirrors with an absolute band gap for all angles of incidence.
The use of metallic
mirrors is limited due to their relatively large absorption at the
visible (Vis) and near infrared (NIR) frequencies.  An attractive alternative
consists of low-absorption dielectric
structures,  which may be designed for specific frequency
ranges. One-dimensional (1D) and two-dimensional (2D) PCs have
applications in optoelectronics, optical telecommunications and computing,
laser technology \cite{Lopez2003,Masaya2010}, and radiative cooling applications
\cite{Kumar2020}. The simplest 1D-PC is composed of a finite number
of periodically alternating
layers of high $n_h$ and low $n_l$ refractive indices, with
corresponding thicknesses $d_h$ and $d_l$ chosen so that their optical
thicknesses corresponds to a quarter of a wavelength
$n_hd_h=n_ld_l=\lambda_{0}/4$ at a nominal
wavelength $\lambda_{0}$. This yields a {\em Bragg mirror} (BM)
which might have a large PBG including an omnidirectional gap if the contrast $n_h/n_l$
and the number of periods are large enough. Mirrors with high
reflectance within a wider frequency range may be engineered by
using different nominal wavelengths for different layers.
One way to obtain such structures is to gradually change the width of
the layers as a function of their depth, producing
\textit{chirped}-type structures \cite{Zipock1997}.
Another alternative is to stack BMs, in such a way that their reflection bands partially
overlap each other at their edges, resulting in a wider high-reflection band \cite{Xifre2009}.

@@

In Fig. \ref{Fig2}(a) we present the calculated and measured
reflectance for non-polarized light corresponding to sample $S_1$ in the spectral range from 350 to 1400
nm for different angles of
incidence $\theta=10^\circ$, $20^\circ$, $30^\circ$, $40^\circ$,
$50^\circ$, and $60^\circ$. The spectra are qualitatively
similar, and for $\lambda>700$ nm and $10^\circ < \theta <
40^\circ$, they agree quantitatively, with a difference smaller
than $5\%$.
The
measured reflectance is lower than the calculated one, more so at
small wavelengths and large angles. This difference
may be partially attributed to the scattering of light due to the
roughness present at the sample
\cite{Theiss1994,Chavez2020,Ortiz2020} that we have not taken into
account in our theory. Due to the limitations of our
spectrophotometer, we couldn't perform measurements for $\theta>60^\circ$ and thus
check the ODB. Nevertheless, our results allow us to conclude that
the structure has a quasi-ODB from 980 and
1340 nm.
\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{F2Alternativa.pdf}
  \end{center}
  \caption{Reflectance spectra for non-polarized light calculated and measured at different
    angles of incidence $\theta=10^\circ$, $20^\circ$, $30^\circ$,
    $40^\circ$, $50^\circ$, and $60^\circ$ for structure $S_1$
    (panel a)  and $S_2$ (panel b). The gray band indicates the
    region where the reflectance is greater than  $90\%$,
    corresponding to the quasi-ODB of the
    structure. Inset: photograph of the synthesized structure.}
  \label{Fig2}
\end{figure}
In Fig. \ref{Fig2}(b) we compare the
calculated and measured spectra of sample $S_2$ in the range
from 400 to 3000 nm.
Both spectra are very similar, with some differences at long
wavelengths which can be
attributed to an increase of imperfections such as wavy layers and
more roughness for deeper layers, due to a more restricted diffusivity
of the electrolyte as the thickness of the structure is increased
\cite{Negro2003,Vincent1993}. According to our results, this
structure has a wide quasi-ODW of 1800 nm
centered at 1880 nm.

@@

According to Table \ref{tab:table2}, the structure that has the highest
reflectance is in the second block, with an optimal overlap between
consecutive PBGs of $78\%$, a thickness of
41.5 $\mu$m, and an average reflectance $\braket{R}=95.4\%$. It is made up
of 18 sub-mirrors tuned to the wavelengths
400, 460, 510, 570, 640, 720, 810, 910, 1020, 1150, 1290, 1450,
1630, 1830, 2060, 2320, 2610, and 2860 nm.
We synthesized this structure and designated it {\em sample $S_3$}.
Its calculated and measured
reflectance spectra are shown in Fig. \ref{Fig3}.
\begin{figure}
        \begin{center}
                \includegraphics[width=\textwidth]
                {F3Alternativa.pdf}
        \end{center}
        \caption{ (a) Calculated reflectance $R(\lambda,\theta)$ for non-polarized light of the optimized structure $S_3$
                as a function of wavelength $\lambda$ and incidence angle
                $\theta$. (b) Measured and calculated reflectance spectra at several
                angles of incidence $\theta=10^\circ$, $20^\circ$,
                $30^\circ$, $40^\circ$, $50^\circ$, $60^\circ$. The gray band indicates
                the region in which the reflectance is greater than $R>90\%$.  Inset shows a
                photograph with a top view of the synthesized structure.}
        \label{Fig3}
\end{figure}

@@

We developed a formalism to design and optimize highly
reflective quasi-omnidirectional multilayered mirrors with a wide
spectral range. We considered two kinds of systems, chirped structures with a gradual
change in layer thicknesses and
stacked Bragg mirrors tuned so that their bandwidths overlap, and
optimized their
reflectance with minimum thickness for a given pair of refractive
indices. Numerical calculations were
carried out employing a stabilized transfer matrix method and we optimized the
design parameters to obtain maximal reflectance averaged over different spectral ranges for
all angles.
We fabricated some of the optimized structures with
porous silicon
dielectric multilayers with low refractive contrast and compared their measured  optical properties
with the calculations. Two chirped structures
with thicknesses 21.6 $\mu$m and 60.4 $\mu$m,
resulting in quasi-omnidirectional mirrors with bandwidths of 360 nm and 1800 nm, centered
at 1160 nm and 1925 nm respectively were shown. In addition,
we fabricated a stacked structure  with a
quasi-omnidirectional bandwidth of 1800 nm centered at 1850 nm and a
thickness of 41.5 $\mu$m, which is almost two thirds as thick as the chirped structure.
Thus, our techniques allowed us to obtain relatively thin
quasi-omnidirectional mirrors with wide bands
over different wavelength ranges that compare favorably to those in
the literature.
We believe that our analysis techniques can
be used for the optimization of the reflectance not only in
multilayered porous silicon systems but also for systems with other types of
materials with low refractive index contrast. The present study could
also be useful for obtaining omnidirectional dielectric mirrors in
large spectral regions using different materials,  flat focusing
reflectors, thermal regulators, or, if
defects are included, as filters or remote chemical/biosensors with
a wide angular independent response.

@@

\bibliography{Bibliografia}
